Effects of Reynolds Number on the Energy Conversion and Near-Wake Dynamics of a High Solidity Vertical-Axis Cross-Flow Turbine

### 2016-01-21 paper.tex
Diameter based --> based on diameter

When designing or studying arrays, it is common to use very small
(geometrically) scaled \mbox{devices \cite{Chamorro2011, Chamorro2011b}}. It is
therefore important to realize the limitations of evaluating both the power
output of turbines and the wake recovery when the Reynolds number is very far from
full scale. Sometimes,~the models used are not turbines, but wake-generating objects,
e.g., porous disks, that are meant to replicate the wakes of real turbines
\cite{Goldenberg1983}. In this case, it is of interest to determine at what
Reynolds number one might be able to realistically study wake flows in an array
and also to evaluate the effectiveness of a wake generator. In other words, a
wake generator may do a fine job simulating a scaled turbine, but how well can
it simulate a full-scale device? Note that for a porous disk, the Reynolds
number of interest is diameter based, since it is the scaling of the far-wake
dynamics that~ matters.

>>>>

When designing or studying arrays, it is common to use very small
(geometrically) scaled \mbox{devices \cite{Chamorro2011, Chamorro2011b}}. It is
therefore important to realize the limitations of evaluating both the power
output of turbines and the wake recovery when the Reynolds number is very far
from full scale. Sometimes,~the models used are not turbines, but
wake-generating objects, e.g., porous disks, that are meant to replicate the
wakes of real turbines \cite{Goldenberg1983}. In this case, it is of interest to
determine at what Reynolds number one might be able to realistically study wake
flows in an array and also to evaluate the effectiveness of a wake generator. In
other words, a wake generator may do a fine job simulating a scaled turbine, but
how well can it simulate a full-scale device? Note that for a porous disk, the
Reynolds number of interest is based on diameter, since it is the scaling of the
far-wake dynamics that~ matters.
